---
title: "ICE"
author: "Sam Burer"
date: "September 20, 2017"
output: html_document
---

```{r echo = FALSE}
url <- "https://data.cityofchicago.org/api/views/kn9c-c2s2/rows.csv"
download.file(url, "data.csv")
indicators <- read.csv("data.csv", stringsAsFactors = FALSE)
```

```{r echo = FALSE, warning = FALSE, message = FALSE}
library(rvest)
url <- "https://en.wikipedia.org/wiki/Neighborhoods_in_Chicago"
pg <- read_html(url)
tb <- html_table(pg, fill = TRUE)
neighborhoods <- tb[[1]]
```

```{r echo = FALSE, warning = FALSE}
library(ggplot2)
library(scales)
p <- qplot(PERCENT.AGED.UNDER.18.OR.OVER.64,
           PER.CAPITA.INCOME,
           data = indicators, geom = "point", color = I("blue"))
p <- p + scale_y_continuous(
  name = "Per Capita Income",
  labels = dollar)
p <- p + scale_x_continuous(
  name = "Percent Aged Under 18 or Over 64")
```

```{r echo = FALSE}
neighborhoods$"Community area" <- as.factor(neighborhoods$"Community area")
df <- as.data.frame(table(neighborhoods$"Community area"))
df <- df[order(df$Freq, decreasing = TRUE), ]
names(df) <- c("Community Area", "Number of Neighborhoods")
```

```{r echo = FALSE}
library(scales)
medpci <- dollar(round(median(indicators$PER.CAPITA.INCOME), 0))

tmp <- max(indicators$PER.CAPITA.INCOME)
tmp <- indicators$PER.CAPITA.INCOME == tmp
maxpci <- indicators$COMMUNITY.AREA.NAME[tmp]

tmp <- min(indicators$PER.CAPITA.INCOME)
tmp <- indicators$PER.CAPITA.INCOME == tmp
minpci <- indicators$COMMUNITY.AREA.NAME[tmp]
```


The City of Chicago has `r nrow(neighborhoods)` neighborhoods, which are organized
into `r nrow(indicators)` community areas. With respect to the community
areas, the median per capita income is `r medpci`. The community area with
the highest per capita income is `r maxpci`, while the community with
the lowest is `r minpci`.

The following table presents the ten largest community areas in terms
of number of neighborhoods:

```{r echo = FALSE, comment = NULL}
print(head(df, n = 10), row.names = FALSE)
```

The following plot presents the relationship between *Per Capita Income*
and *Percent Aged Under 18 or Over 64* in the community areas
of Chicago:

```{r echo = FALSE, comment = NULL}
p
```
